Model to study co-evolution of trade an culture

### 2015-03-23 article.tex
notes on article read from economics of ancient cultures
start to rewrite state of the art trade

\title{Model to study co-evolution of trade an culture}

@@

\maketitle

@@

Multiple approaches have been proposed to model the economical interactions in the ancient mediteranean culture. Among these we will focus on the formal models. These are close to our works, can be tested and compared.

%Hopkins 1980: structure of tax system. two hypothesis. 1)taxation increased volume of trade in the empire? 2) tax-exporting province (recently integrated province) had to export to pay tax. roman supported by many small taxes. Not sure to cite it, goes to much more
%Termin 2001: based on multiple consideration classify roman economy as market based with loose tie from things far appart. composed of local markets connected together
%Terpstra 2011: micro economic model to explain possibility of trade in roman empire under uncertainty. based on reputation in the network and removal of bad from the network (personalized network based on geographical info). focus on a specific case (one city and its relations with others). threat of expulsion or loss of reputation as reinforcement <- not only economic.

>>>>

\title{Model to study co-evolution of trade an culture}
\maketitle

@@

@@

Multiple approaches have been proposed to model the economical interactions in the ancient Mediterranean culture. Among these we will focus on the formal models. These are close to our works, can be tested and compared.

Hola chicos, our goal is to understand the interaction between trade exchange and cultural evolution in the mediteranean societies. Therefore we start by looking at the work studying the economy in the mediteraneean word
\todo{list of works and that none of them generate stuff}

%Hopkins 1980: structure of tax system. two hypothesis. 1)taxation increased volume of trade in the empire? 2) tax-exporting province (recently integrated province) had to export to pay tax. roman supported by many small taxes. Not sure to cite it, goes to much more

%Termin 2001: based on multiple consideration classify roman economy as market based with loose tie from things far appart. composed of local markets connected together

%Terpstra 2011: micro economic model to explain possibility of trade in roman empire under uncertainty. based on reputation in the network and removal of bad from the network (personalized network based on geographical info). focus on a specific case (one city and its relations with others). threat of expulsion or loss of reputation as reinforcement <- not only economic.

%quantifying roman economy 2009: collections of work on roman economy. Study of the integratedness of the roman economy. How the enforcement and so on were working ? Hard to find global vision <- maybe because there was none. More inter-connected stuffs
%  even pattern of currency is complex. diff between west and east
%  Approaches to Quantifying Roman Trade: try different stuff on different goods. 
%    little prospect of quantifying vague notions of ‘trade’. need to brake the question in sub questions. in all data some biases that have to be cleared
%  Response to Andrew Wilson: need to put findings in context. look from the point of view of the costumer

%A Model of Real Income Growth in Roman Italy, scheidel, 2007 : constraint on pop growth from different factors. massive redistribution that raised household wealth. raising income of sub-elite in italia.
%  model: well just with words and a table listing the different factors on income and their effect varying with time

%The organization of the grain trade in the early Roman Empire, 2007: problem of importation of grain to roman cities. use of variety of mechanisms to deal with problems of long-distance trade

%In Search of Roman Economic Growth, 2008: relate proxy indice to economic performance <- maybe read

%The economy of the early roman empire, 2006: market perspective on roman history.

%Monitoring regional market systems in prehistory: Models, methods, and metrics, 2005
%  claim that model produced is testable. model of distribution of commodity distribution under different market system organisaton. To check in details. 
%  argue that markets have a central role on the organisation of ancient societes and that they have been rarely studied. need measure to model and monitor regional organisation. here measure distribution of goods on the market. case study on aztec.

% Central place theory <- prediction of working of settlements. link to dynamic version and Spatial Interactions Models

Therefore another way to tackle the review is to know if someone appears to have studied the use of MAS to create models of early economies. The stuff on anasazi is a famous modelisation of early cultures but they don't study the trading part. However in the Pueblo project they look at the modelisation of an early society from various angle including trade and cultural transmission. They are for example interested in the competition between various trade mechanisms and the emergence of inequalities However there are two limitations on the works done: they consider a pre-market society which clearly doesn't exhibit the same dynamics. The study also takes place in the village framework which makes it hard to extract the conclusions reached on the economy from the global framework.

%lake 2014:
%  take the third paragraph of lake 2014 for the description of MAS for archaeology
%  we are not interested in the end result but how certain process works and what sort of change could have happen.

%Dean 2000: famous anasazi model. in sugarscape, no trading.

%Kohler 2012: travail sur pueblo societies, and some stuff on trading. Stuff on trading are actually super close to us. They look also at political hierarchy
%Cockburn :
% operate in proto-market economy while we aim to test market.
% they look at specialization

%kobti 2012 la meme que kobti 2006 ?
%	pour 2006: etude de l'apparition d'inegalite

%cockburn: specialisation avec une machine a gaz

% smith and choi 2007 (pas sur de citer)
%  model of inequalities
%	start with two models of interaction mostly mutualistic and end up with inequalities
